Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-17 pkg/disttree/inst/draft/rejoinder.Rnw
some more revision based on reviews and feedback
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2332 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4e2046f29218da7c2bc2cc048097a096f6a0157b
some more revision based on reviews and feedback
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2333 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 23f1b1b3a505c4e3312e7057cde6de6cbeedeb4a

The skewness results from the characteristics of precipitation sums. 
Most of the time no or only moderate precipitation amounts are forecasted 
and observed. In some situations (e.g., days with thunderstorms, cold and 
warm fronts, \dots) large amounts of precipitation can be observed at 
specific sites. This is often also depict by the ensemble prediction 
system where a subset of all members predicts rather large amounts 
(compared to the overall ensemble mean or median). This yields strongly 
skewed ensemble forecasts which has to be addressed in some sort.\\
\fixme{\textit{FIXME: Should this explanation why there is skewness be included?}}

As you mention one way how to deal with skewness would be to 
apply a distributional family with an additional parameter to capture
skewness. However, this can be very complex and thus lead to less well 
fitting estimators of the location and scale parameter.
Moreover, the focus of this paper is on the features of the presented 
distributional forest regarding variable selection and the capability 
to also model non-linear effects rather than optimizing the model 
specification for this particular application.
Transforming the data to remove large parts of the skewness is
a frequently used approach. Therefore, employing such a transformation 
allows for a better way of comparing our results to those presented in 
literature. In this study we are thus following Stauffer et al. (2017) 
using the power transformation which turned out to be optimal 
for a similar application for the very same study area.

@@

We completely agree with you as that other models such as
GAMLSS are clearly advantageous regarding interpretability. 
These models provide a very powerful framework that works
well in a wide range of applications and research fields, 
including meteorology. Therefore, our intention is not to present 
distributional forests as a replacement of these commonly used methods 
but rather as a well working alternative. Especially if one is mainly 
interested in predictive skill and a good performing fully automated 
weather forecasting tool the interpretability is not implicitly needed 
in some cases (machine learning performance vs. interpretability).
We adapted our manuscript as we definitely want to emphasize that in our 
application the focus is mainly on prediction but not on interpretation. 
We hope we could point this out clearly. \\
\fixme{\textit{FIXME: Where should this be pointed out in the manuscript? Discussion?}}

@@

\begin{review}
8. I found the competing models to be chosen pretty unfair. 
First, for the prespecified GAMLSS, the authors use 
”relevant effects based on expert knowledge”. Why not all? 
Why not making a decision on some information criteria such as AIC/BIC? 
The latter would be done if the analyst decided to use a prespecified 
GAMLSS. I guess, the GAMLSS could improve a lot by this . 
\end{review}

@@

>>>>

As you mention one way to deal with skewness is to use a distribution
with an additional skewness parameter (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016) which increases the complexity of the statistical
models.
Another frequently used approach is to apply a
power-transformation (Stidd 1973, Hutchinson 1998, Stauffer et al. 2017) to
remove the majority of the skewness from the data. The optimal transformation
depends on the application and data set, in our case we are following the work
of Stauffer et al. (2017) who presented a similar application on the very same
data set. As our results show (Figure~3 in the manuscript) this approach works 
well for the application presented in our manuscript.
Moreover, the focus of this paper is on the features of the presented
distributional forest regarding variable selection and the capability
to also model non-linear effects rather than optimizing the model
specification for this particular application.

%The skewness results from the characteristics of precipitation sums. 
%Most of the time no or only moderate precipitation amounts are forecasted 
%and observed. In some situations (e.g., days with thunderstorms, cold and 
%warm fronts, \dots) large amounts of precipitation can be observed at 
%specific sites. This is often also depict by the ensemble prediction 
%system where a subset of all members predicts rather large amounts 
%(compared to the overall ensemble mean or median). This yields strongly 
%skewed ensemble forecasts which has to be addressed in some sort.\\
%\fixme{\textit{FIXME: Should this explanation why there is skewness be included?}}

%As you mention one way how to deal with skewness would be to 
%apply a distributional family with an additional parameter to capture
%skewness. However, this can be very complex and thus lead to less well 
%fitting estimators of the location and scale parameter.
%Moreover, the focus of this paper is on the features of the presented 
%distributional forest regarding variable selection and the capability 
%to also model non-linear effects rather than optimizing the model 
%specification for this particular application.
%Transforming the data to remove large parts of the skewness is
%a frequently used approach. Therefore, employing such a transformation 
%allows for a better way of comparing our results to those presented in 
%literature. In this study we are thus following Stauffer et al. (2017) 
%using the power transformation which turned out to be optimal 
%for a similar application for the very same study area.

@@

We completely agree with you as that other models such as
GAMLSS are clearly advantageous regarding interpretability.
These models provide a very powerful framework that works
well in a wide range of applications and research fields,
including meteorology. Therefore, our intention is not to present
distributional forests as a replacement of these commonly used methods
but rather as a well working alternative. Especially if one is mainly
interested in predictive skill and a good performing fully automated
weather forecasting tool the interpretability is not implicitly needed
in some cases (machine learning performance vs. interpretability, e.g.,
Rasp and Lerch 2018).
We adapted our manuscript as we want to emphasize that in our
application the focus is mainly on the predictive performance and less on
the interpretation of the different effects.
We hope we could point this out clearly. \\
\fixme{\textit{FIXME: Where should this be pointed out in the manuscript? 
In the discussion or after introducing trees and forests? (trade-off between
flexibility of the model and interpretability)}}

@@

\begin{review}
8. I found the competing models to be chosen pretty unfair. 
First, for the prespecified GAMLSS, the authors use ``relevant effects based on expert knowledge''. Why not all? 
Why not making a decision on some information criteria such as AIC/BIC? 
The latter would be done if the analyst decided to use a prespecified 
GAMLSS. I guess, the GAMLSS could improve a lot by this . 
\end{review}

@@

\item[] Scheuerer, M. and Hamill T. M. (2015). Statistical Postprocessing of
Ensemble Precipitation Forecasts by Fitting Censored, Shifted Gamma
Distributions,
\textit{Monthly Weather Review} \textbf{143, 11}: 4578--4596.
%doi:10.1175/MWR-D-15-0061.1

\item[] Baran, S., and Nemoda, D. (2016). Censored and Shifted Gamma Distribution Based EMOS
Model for Probabilistic Quantitative Precipitation Forecasting,
\textit{Environmetrics}, \textbf{27}: 280--292.
%doi: 10.1002/env.2391.

\item[] Hutchinson M. F. (1998). Interpolation of Rainfall Data with Thin
Plate Smoothing Splines -- Part II: Analysis of Topographic Dependence,
\textit{Journal of Geographic Information and
Decision Analysis} \textbf{2, 2}: 152--167.
%doi:10.1080/02693799508902045

\item[] Stidd, C. K. (1973). Estimating the Precipitation Climate,
\textit{Water Resources Research}, \textbf{9, 5}: 1235--1241.
%doi:10.1029/wr009i005p01235
\end{itemize}
